---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  dpi = 300,
  fig.path = "man/figures/README-",
  fig.width = 7,
  out.width = "100%"
)
```

# sagethemes

<!-- badges: start -->
[![R build status](https://github.com/Sage-Bionetworks/sagethemes/workflows/R-CMD-check/badge.svg)](https://github.com/Sage-Bionetworks/sagethemes/actions)
<!-- badges: end -->

The sagethemes package provides plot color palettes and themes that use the Sage
Bionetworks branded colors.

## Installation

```{r install, eval = FALSE}
remotes::install_github("Sage-Bionetworks/sagethemes")
```

## Colors

Colors were developed by the Sage design team and are available in the list
`sage_colors`.

```{r color-list}
library("sagethemes")
str(sage_colors, list.len = 5)
```

## Usage

sagethemes provides continuous, discrete, and binned scales.

```{r discrete}
library("ggplot2")
library("sagethemes")

ggplot(mpg, aes(displ, hwy, colour = class)) +
  geom_point() +
  scale_color_sage_d()
```

```{r continuous}
ggplot(faithfuld, aes(waiting, eruptions, fill = density)) +
  geom_tile() +
  scale_fill_sage_c(option = "powder")
```

---

## Code of Conduct

Please note that the dccvalidator project is released with a [Contributor Code
of Conduct](.github/CODE_OF_CONDUCT.md). By contributing to this project, you
agree to abide by its terms.
