---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  dpi = 300,
  fig.path = "man/figures/README-",
  fig.width = 7,
  out.width = "100%"
)
```

# sagethemes

<!-- badges: start -->
[![R build status](https://github.com/Sage-Bionetworks/sagethemes/workflows/R-CMD-check/badge.svg)](https://github.com/Sage-Bionetworks/sagethemes/actions)
<!-- badges: end -->

The sagethemes package provides plot color palettes and themes that use the Sage
Bionetworks branded colors.

## Installation

```{r install, eval = FALSE}
remotes::install_github("Sage-Bionetworks/sagethemes")
```

## Colors

Colors were developed by the Sage design team and are available in the list
`sage_colors`.

```{r color-list}
library("sagethemes")
head(sage_colors, n = 3)
```

## Usage

sagethemes provides continuous, discrete, and binned scales.

```{r discrete}
library("ggplot2")
library("sagethemes")

# discrete
ggplot(mpg, aes(displ, hwy, colour = class)) +
  geom_point() +
  scale_color_sage_d()
```

```{r continuous}
# continuous
ggplot(faithfuld, aes(waiting, eruptions, fill = density)) +
  geom_tile() +
  scale_fill_sage_c(option = "powder")
```

```{r binned}
# binned
ggplot(faithfuld, aes(waiting, eruptions, fill = density)) +
  geom_tile() +
  scale_fill_sage_b(option = "powder")
```

## Fonts

Sage Bionetworks uses [Lato](http://www.latofonts.com/lato-free-fonts/). If
you've installed Lato on your system, you should be able to use it in plots.

However, to output to PDF, PostScript, or bitmap files on Windows, you need to
register the font. sagethemes includes a copy of Lato, and you can load it with
`import_lato()`. If saving to PDF you'll also need to embed Lato in the PDF
file.

```{r lato, eval = FALSE}
import_lato()

p <- ggplot(mpg, aes(displ, hwy, colour = class)) +
  geom_point() +
  scale_color_sage_d() +
  theme_gray(base_family = "Lato")

# Save PDF plot and embed Lato font
ggsave("plot.pdf", plot = p)
embed_fonts("plot.pdf", outfile = "plot_embed.pdf")
```

---

## Code of Conduct

Please note that the dccvalidator project is released with a [Contributor Code
of Conduct](.github/CODE_OF_CONDUCT.md). By contributing to this project, you
agree to abide by its terms.
